Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2015-06-03 tex/parametrized-learning-aoas.tex
text about embedding s in p

In most settings that make use of likelihood ratio tests, the likelihood is based directly on some approximation of density for the observed data via $\hat{f}(x|\theta)$.  In general, approximating the density $\hat{f}(x|\theta)$ is difficult for high-dimensional data, which motivates the use of the dimensionality reduction map $\hat{s}(x)$ and likelihood ratio tests based on the univariate density $\hat{g}(\hat{s}|\theta)$.  In the case of a fixed classifier $\hat s(x)$ it is possible to pre-compute $\hat s_e=\hat s(x_e)$ and never refer back to the original features $x_e$. In the parametrized setting it is not possible to pre-compute $\hat s(x_e; \theta_0, \theta_1)$ for all values of $\theta_0$ and $\theta_1$; however, we can  embed the classifier into the likelihood function to carry out the composition $\hat{g}\circ \hat{s}$. A concrete realization of this has been performed for probability models implemented with the \texttt{RooFit} probabilistic programing language and  classifiers implemented with \texttt{scikit-learn} and \texttt{TMVA}~\citek{Verkerke:2003ir,scikit-learn,Hocker:2007ht}.

>>>>

In most settings that make use of likelihood ratio tests, the likelihood is based directly on some approximation of density for the observed data via $\hat{f}(x|\theta)$.  In general, approximating the density $\hat{f}(x|\theta)$ is difficult for high-dimensional data, which motivates the use of the dimensionality reduction map $\hat{s}(x)$ and likelihood ratio tests based on the univariate density $\hat{g}(\hat{s}|\theta)$.  In the case of a fixed classifier $\hat s(x)$ it is possible to pre-compute $\hat s_e=\hat s(x_e)$ and never refer back to the original features $x_e$. In the parametrized setting it is not possible to pre-compute $\hat s(x_e; \theta_0, \theta_1)$ since one does not know the true values of  $\theta_0$ and $\theta_1$; however, we can  embed the classifier into the likelihood function to carry out the composition $\hat{g}\circ \hat{s}$. A concrete realization of this has been performed for probability models implemented with the \texttt{RooFit} probabilistic programing language and  classifiers implemented with \texttt{scikit-learn} and \texttt{TMVA}~\citek{Verkerke:2003ir,scikit-learn,Hocker:2007ht}.
